---
title: "cdogma"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{cdogma}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

GitHub repository:https://github.com/s223102/group_17_cdogma 

The cdogma package helps you convert your DNA sequence into a protein, replicating the central dogma in biology. 
It can also be used to simulate a DNA strand of x length for training purposes.
Finally, it can provide you with a great visualization of the amino acid composition encoded in the input DNA sequence.

```{r setup}
library(cdogma)

```


***Typical use case:***

Step 0   Generate random DNA sequence with set length (optional)
```{r} 
DNA <- create_string(size=100)
```

Step 1    Convert the DNA (coding strand) input to mRNA
```{r}
mRNA <- dna_to_rna(DNA)
```

Step 2    Convert the mRNA to a vector of codons
```{r}
# load the codon translation table
load("~/cdogma/R/sysdata.rda")
vector_of_codons <- rna_to_codons(mRNA)
```

Step 3    Convert the vector of codons to a protein sequence
```{r}
protein <- translate(vector_of_codons)
```

Step 4    Visualize the amino acid distribution in the protein
```{r}
bar_chart <- count_aa(protein)
bar_chart
```

***Discussion of dependencies***
Limiting the number of dependencies in a package is generally a good idea because it reduces the risk of conflicts between packages, and it may improve performance (loading time in particular). However, if the package requires functionality not in base R, dependencies can be necessary.

***Discussion on difference between @importFrom and package::function()***
Generally @importFrom adds a specific function frmo a package to the namespace of ones pacakge without loading the entire package, whereas package::function() calls a specific function from a pacakge but does not add it to the name space, and hence must the package:: prefix must be used every time the function is called. It is good practice to specify the package as prefix, but it can be tiresome if a package heavily depends on a specific function. 
